working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-03-12 Manuscript_draft/Manuscript_draft.tex
edits

\begin{figure}
\centering
\includegraphics{output/figures/unnamed-chunk-7-1.pdf}
\caption{The effect of heterospecific pollen (scaled see set) is
represented in function of the compatibility system (self/cross*100) for
the the different species. Each coulored dot represents the interaction
of a focal species with a different pollen donor.}
\end{figure}

\href{Jose}{Compatibility index don´t multiply per 100 from Lloyd}

@@

Discussion

@@

\includegraphics{output/figures/unnamed-chunk-9-1.pdf}
\includegraphics{output/figures/unnamed-chunk-9-2.pdf}
\includegraphics{output/figures/unnamed-chunk-9-3.pdf}

>>>>

@@

Although we have found a positive correlation between phylogenetic
distance and heterospecific pollen effect, this results have to be
treated carefully. From our results we want to highlight that also far
related species can affect negatively fitness but the effect from close
related is species can also have important detrimental effects.
Moreover, the effect of close related species can be masked by the
possibility of hibridization as it occure between two of our species of
Brassica. Moreover, although different effect between distinct donors
can occur we want to note the importance on the traits of the recipient
that determine an homogeneous effect between donors. These different
traits will define how it will be the effect across the different
species independently of the nature of the donor. Although traditionally
the nature of the pollen donor have been very studied, the
recipient\ldots{}

@@

\includegraphics{output/figures/unnamed-chunk-8-1.pdf}
\includegraphics{output/figures/unnamed-chunk-8-2.pdf}
\includegraphics{output/figures/unnamed-chunk-8-3.pdf}
